Preregistration

### 2021-05-10 preregistration.Rmd
simplify simulation

```{r setup, include=FALSE}
library(tidyverse)
library(lavaan)
library(furrr)
library(slider)
library(patchwork)
source(here::here("R", "simulation.R"))
# if you have access to a hpc envir specify this in R/hpc.R
# if not we use local multicore
# to speed up consider reduce nsim; increase nstep in ↑YAML↑

@@

```{r models}
true_diff <- 0.2
model_truth <- combine(
  measurement(
    "MACH",
    items("x", 9),
    loadings = round(loadings_jones_paulhus * 0.7, 2)
  ),
  intercepts("MACH", list(0, true_diff)),
  variances("MACH", list(1, 1))
)

model_same <- 
  "MACH =~ x1 + x2 + x3 + x4 + x5 + x6 + x7 + x8 + x9
  MACH ~ c(0,0)*1
  MACH ~~ c(1, NA)*MACH"

model_differ <- 
  "MACH =~ x1 + x2 + x3 + x4 + x5 + x6 + x7 + x8 + x9
  MACH ~ c(0, NA)*1 + c(zero, diff)*1
  MACH ~~ c(1, NA)*MACH"
```

```{r sim}
extract_fns <- list(bic = get_bic, 
                    aic = get_aic,
                    lrt_p = get_lrt_p,
                    delta_p = get_delta_p,
                    estimate = get_estimate,
                    std_delta_p = get_std_delta_p,
                    std_estimate = get_std_estimate)

n_obs <- seq(params$nmin, params$nmax, params$nstep)
n_sim <- params$nsim

setup <- expand_grid(n_obs = n_obs,
                     truth = model_truth,
                     same = model_same,
                     differ = model_differ,
                     mod_load = c(3),
                     mod_int = c(3),
                     extract_fns = list(extract_fns),
                     group.equal = list(c("loadings", "intercepts")),
                     auto.fix.first = FALSE)
to_export <- ls_funs() %>% map(get)
to_export <- c(list(setup = setup), to_export)
RNGkind("L'Ecuyer-CMRG")
set.seed(params$seed)
seed <- params$seed
res_raw %<-% generate_data_setup(n_sim,
                setup,
                furrr_options(
                  globals = to_export,
                  seed = seed,
                  packages = c("furrr", "lavaan", "tidyverse")
                ))
```

@@

```{r}
res <- res_raw  %>%
  map(bind_rows) %>% 
  bind_rows() %>% 
  mutate(results = map(results, "result")) %>% 
  unnest(results)

res <- mutate(
  res,
  dec_bic = bic < 0,
  dec_aic = aic < 0,
  dec_aic2 = aic < -2,
  dec_lrt_p = lrt_p < 0.05,
  dec_delta_p = delta_p < 0.05)

res_interval <- res %>%
  select(n_obs, std_estimate, mod_load, mod_int) %>% 
  filter(!is.na(std_estimate)) %>% 
  group_by(n_obs, mod_load, mod_int) %>% 
  summarise(interval = list(interval(std_estimate, seq(0.05, .2, 0.01))), 
            .groups = "drop", median = median(std_estimate)) %>% 
  unnest(c(interval)) %>% 
  mutate(width = upper - lower, perc = 1 - alpha) %>% 
  group_by(alpha) %>% 
  arrange(n_obs) %>% 
  mutate(across(c(width, upper, lower),
                ~slide_dbl(.x, mean, na.rm = TRUE, .before = 2, .after = 0, .complete = FALSE))) %>% 
  ungroup() %>% 
  arrange(perc)
```

```{r}
choosen_perc <- .8
choosen_width <- .2
minn <- filter(res_interval, perc == choosen_perc, width < choosen_width) %>% 
  filter(n_obs == min(n_obs))
```

@@

```{r}
plot_interval +
  theme(axis.text.x = element_blank(), axis.title.x = element_blank()) + 
  plot_width +
  plot_layout(nrow = 2, guides = 'collect') +
  plot_annotation(tag_levels = 'A')
ggsave("plot.svg", device = svglite::svglite, width = 7, height = 4)
```

>>>>

```{r setup, include=FALSE}
library(tidyverse)
library(lavaan)
library(furrr)
library(slider)
library(patchwork)
source(here::here("R", "simulation.R"))
repro::automate_load_scripts()
# if you have access to a hpc envir specify this in R/hpc.R
# if not we use local multicore
# to speed up consider reduce nsim; increase nstep in ↑YAML↑

@@

```{r sim}
n_obs <- seq(params$nmin, params$nmax, params$nstep)
n_sim <- params$nsim
# n_sim * length(n_obs)
# [1] 100000
to_export <- ls_funs() %>% map(get)
to_export <-
  c(to_export, list(
    n_obs = seq(params$nmin, params$nmax, params$nstep),
    n_sim = params$nsim
  ))
res_raw %<-% simulation_study(n_obs, n_sim,
                furrr_options(
                  globals = to_export,
                  seed = seed,
                  packages = c("furrr", "lavaan", "tidyverse")
                ))
```

@@

```{r}
res <- res_raw %>% mutate(n_obs = as.numeric(n_obs))
res_interval <- res %>%
  select(n_obs, std_estimate) %>% 
  filter(!is.na(std_estimate)) %>% 
  group_by(n_obs) %>% 
  summarise(interval = list(interval(std_estimate, seq(0.05, .2, 0.01))), 
            .groups = "drop", median = median(std_estimate)) %>% 
  unnest(c(interval)) %>% 
  mutate(width = upper - lower, perc = 1 - alpha) %>% 
  group_by(alpha) %>% 
  arrange(n_obs) %>% 
  mutate(across(c(width, upper, lower),
                ~slide_dbl(.x, mean, na.rm = TRUE, .before = 2, .after = 0, .complete = FALSE))) %>% 
  ungroup() %>% 
  arrange(perc)
```

```{r}
choosen_perc <- .8
choosen_width <- .2
true_diff <- .2
minn <- filter(res_interval, perc == choosen_perc, width < choosen_width) %>% 
  filter(n_obs == min(n_obs))
```

@@

```{r}
simulation_plot <- plot_interval +
  theme(axis.text.x = element_blank(), axis.title.x = element_blank()) + 
  plot_width +
  plot_layout(nrow = 2, guides = 'collect') +
  plot_annotation(tag_levels = 'A')
simulation_plot
write_rds(simulation_plot, "simulation_plot.rds")
ggsave("simulation.svg", device = svglite::svglite, width = 7, height = 4)
```
